Introduction to Markov state modeling with the PyEMMA software --- v\versionnumber

### 2018-07-24 manuscript.tex
a few latex changes; updated pdf

The underlying software stack for running the tutorial importantly consists of:
\begin{itemize}
% \item NumPy -- vectorized operations on multi-dimensional arrays~\cite{numpy}
% \item SciPy -- linear algebra, sparse computations~\cite{scipy}
% \item Matplotlib -- Visualization~\cite{matplotlib}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter notebook tool used for running the tutorials~\cite{jupyter}, along with extension packages jupyter_contrib_nbextensions and nbexamples
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nguyen2017nglview}
% \item mdtraj -- reading MD simulation data, calculate observables from MD~\cite{mdtraj}
\end{itemize}

@@

\section{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
CW, MKS, TH, SO, and FN designed research.
CW, MKS, TH, SO, and BHE developed and tested notebooks.
MKS developed the software infrastructure, test, and install environment.
CW, MKS, TH, BEH, and FN wrote the manuscript.

>>>>

The underlying software stack for running the tutorial importantly consists of:
\begin{itemize}
% \item NumPy -- vectorized operations on multi-dimensional arrays~\cite{numpy}
% \item SciPy -- linear algebra, sparse computations~\cite{scipy}
% \item Matplotlib -- Visualization~\cite{matplotlib}
\item \textbf{PyEMMA} -- MSM/HMM estimation, validation, analysis, and visualization, and its dependencies~\cite{pyemma}
\item mdshare -- A downloader for MD data from a public server
\item notebook -- The Jupyter notebook tool used for running the tutorials~\cite{jupyter}, along with extension packages jupyter\_contrib\_nbextensions and nbexamples
\item nglview -- Widget for active viewing of molecular structures in Jupyter environments~\cite{nguyen2017nglview}
% \item mdtraj -- reading MD simulation data, calculate observables from MD~\cite{mdtraj}
\end{itemize}

@@

\section{Author Contributions}
%%%%%%%%%%%%%%%%
% This section mustt describe the actual contributions of
% author. Since this is an electronic-only journal, there is
% no length limit when you describe the authors' contributions,
% so we recommend describing what they actually did rather than
% simply categorizing them in a small number of
% predefined roles as might be done in other journals.
%
% See the policies ``Policies on Authorship'' section of https://livecoms.github.io
% for more information on deciding on authorship and author order.
%%%%%%%%%%%%%%%%
CW, MKS, TH, SO, and FN designed research.
CW, MKS, TH, BEH, and SO developed and tested notebooks.
MKS developed the software infrastructure, test, and install environment.
CW, MKS, TH, BEH, and FN wrote the manuscript.
